---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


[![Travis-CI Build Status](https://travis-ci.org/hughjonesd/pastapi.svg?branch=master)](https://travis-ci.org/hughjonesd/pastapi)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/hughjonesd/pastapi?branch=master&svg=true)](https://ci.appveyor.com/project/hughjonesd/pastapi)
[![Coverage status](https://codecov.io/gh/hughjonesd/pastapi/branch/master/graph/badge.svg)](https://codecov.io/github/hughjonesd/pastapi?branch=master)

# pastapi

`pastapi`, pronounced "Pasta Pi", is a small R package to explore the past API of functions in CRAN packages.
It is designed to help you work out minimum version requirements for packages mentioned in your DESCRIPTION file.

`pastapi` works by downloading package versions from MRAN and temporarily installing them. So, results can 
be slow!

## Example

From [huxtable](https://github.com/hughjonesd/huxtable)'s NEWS file, version 3.0.0:

* New `quick_xlsx` function.

```{r options, include = FALSE}
library(pastapi)
set_lib_dir("~/.pastapi")
```

```{r example}
library(pastapi)
fn_exists_at("quick_xlsx", "huxtable", "3.0.0")
fn_exists_at("quick_xlsx", "huxtable", "2.0.2")
fn_first_exists("quick_xlsx", "huxtable")
```

From the same place:

* New `tidy_args` argument to huxreg allows per-model customization of the call to `tidy`.

```{r example2}

api_same_at("huxreg", "huxtable", "3.0.0")
api_same_at("huxreg", "huxtable", "2.0.2")
api_first_same("quick_xlsx", "huxtable")
```
