---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


[![Travis-CI Build Status](https://travis-ci.org/hughjonesd/apicheck.svg?branch=master)](https://travis-ci.org/hughjonesd/apicheck)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/hughjonesd/apicheck?branch=master&svg=true)](https://ci.appveyor.com/project/hughjonesd/apicheck)
[![Coverage status](https://codecov.io/gh/hughjonesd/apicheck/branch/master/graph/badge.svg)](https://codecov.io/github/hughjonesd/apicheck?branch=master)

# apicheck

`apicheck` is a small R package to explore the historical API of functions in CRAN packages.
It is designed to help you work out minimum version requirements for packages mentioned in your DESCRIPTION file.

`apicheck` works by downloading package versions from CRAN and temporarily installing them in a special directory. 

# Installation

```{r, eval = FALSE}
install.packages("remotes") 
# You'll need these:
remotes::install_github("hughjonesd/rcheology")
remotes::install_github("r-lib/itdepends")

remotes::install_github("hughjonesd/apicheck")
```


# Example

From [clipr](https://github.com/mdlincoln/clipr/)'s NEWS file:

`clipr 0.4.0` introduces `dr_clipr()`:

```{r options, include = FALSE}
library(apicheck)
set_lib_dir(".apicheck")
options(repos = "https://cloud.r-project.org")
```

```{r example}
library(apicheck)
fun_exists_at("clipr::dr_clipr", "0.4.0")
fun_exists_at("clipr::dr_clipr", "0.3.3")
when_fun_exists("clipr::dr_clipr", report = "brief") # binary search
```

`clipr 0.2.0` : several changes to `write_clip`.

```{r example2, warning = FALSE}

api_same_at("clipr::write_clip", "0.2.0")
api_same_at("clipr::write_clip", "0.1.1")
when_api_same("clipr::write_clip", report = "full", search = "all") # check all versions
```

To dig more deeply:

```{r fun-example}
args(fun_at("clipr::write_clip", "0.1.1"))
args(fun_at("clipr::write_clip", "0.2.0"))
help_at("clipr::write_clip", "0.1.1") 
```


To see all changes between two versions, use `compare_versions`:

```{r compare-example, warning = FALSE}
cv <- compare_versions("clipr", "0.1.1", "0.2.0")
summary(cv)
```

You can also check base packages, using the info from [rcheology](../rcheology):

```{r base}
fun_exists_at("base::paste0", "2.14.0")
fun_exists_at("base::paste0", "2.15.0")
```

# Performance

[Performance tests](https://hughjonesd.github.io/apicheck/performance2.html).
